---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette will introduce you to basic functionalities of `enumeR` package.


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(enumeR)
```

First we create some `enum_type` object. It represents a class with finite number of possible values - similliar to enums from other languages like `C++` or `Java`. During construction of an object besides names of values you can specify values of own fields that will be kept inside values. For example:

```{r example}
season_of_year <- enum_type("season_of_year", 
                            c("SPRING", "SUMMER", "AUTUMN", "WINTER"),
                            min_temperature = c(-13, 7, -6, -20),
                            max_temperature = c(20, 32, 18, 12))

print(season_of_year)
```

Now you can access values of this type:

```{r access}
my_favourite_seasons <- season_of_year[c(1,4)]
my_hated_seasons <- season_of_year[c("SUMMER","AUTUMN")]
holiday_season <- season_of_year$SUMMER
```

... but cannot modify it:
```{r modif, error=TRUE}
season_of_year$SUMMER <- "something"
```

You can also choose a random subset:
```{r sample}
sample_seasons <- sample_enum(season_of_year)
```

Objects have thier own classes, which can be checked:
```{r class}
class(season_of_year)
class(holiday_season)
is.enum_type(season_of_year)
is.enum_value(holiday_season)
```

You can add methods to `enum_type` which will be accessing its fields. You can access these fields using their names with dot before it. Thus it's not recommended to add fields which names begin with dot.
```{r methods}
add_enum_methods(season_of_year,
                 temperature_diff = function() {
                   .max_temperature - .min_temperature
                 })

get_enum_method(holiday_season, temperature_diff)()

```
